\section{Communication}
\label{sec:communication}
%how people in the lab talk to each other; things like "always use Slack", "phone calls are only for emergencies"; how long to wait before nudging the PI on something you need; how meetings with PI work and what to prepare for them; check-ins/stand-ups/huddles


\subsubsection{Slack}
Slack is the primary mode
of communication for the CARG,
through \href{http://ucsc-comp-astro.slack.com}{ucsc-comp-astro.slack.com}.
Ask Brant for an invitation.

\subsubsection{Email}
We maintain a group email
list \href{mailto:comp-astro-group@ucsc.edu}{comp-astro-group@ucsc.edu}.
We will use this email list for
announcements. Your UCSC email
will be signed up for a variety
of other lists managed by the
university and department.

\subsubsection{Response Timeline}
Expectations for CARG member
communications on a reasonable timescale, typically within
24 hours for email and as
permitting via Slack.
We do not expect communications
from CARG members after business
hours, over the weekend, or
on holidays. If you receive
communications from Brant or
another CARG member outside of
business hours, please assume
it is because
they had the opportunity
to do so and not because they
expect you to communicate during
those times.

\subsubsection{Websites}
Please develop and maintain a
professional website. A good
option is a GitHub.io site (for
instance, Brant's \href{http://brantr.github.io}{github.io site}).
There is a 
\href{http://robertson.sites.ucsc.edu}{UCSC Computational Astrophysics Research Group website}. We can
cross-link sites as desired.
