\section{Finances \& Reimbursements}
\label{sec:finances}

The CARG is funded primarily by
NASA,
the National Science Foundation,
and Hubble and James Webb Space
Telescope-related grants. 

\subsubsection{Accounts}
For reference, here is a listing of some the CARG accounts and FOAPALs.
\begin{itemize}
\item NSF MRI 81428-443162
\item NASA ATP 83290-443162
\item JWST NIRCam 63513-443162
\end{itemize}

For reference, here as some now-defunct FOAPALS from previous projects:

\begin{itemize}
\item WFIRST 83263-443162
\item LACES 58437-443162
\end{itemize}

\subsubsection{Travel Reimbursements}

Always get pre-approval from 
Brant on travel,
including conference fees,
flight arrangements, 
hotel arrangements, etc. 
University policies related to
travel can be found at \href{https://financial.ucsc.edu/Pages/Travel_Process.aspx}{https://financial.ucsc.edu/Pages/Travel\_Process.aspx}. These resources
supersede any of Brant's 
understandings of reimbursement
policies.\\

\subsubsection{CruzFly}

\noindent
Perhaps the most important form is now 
\href{http://cruzfly.ucsc.edu/}{CruzFly}, which
you will need to request most reimbursements.
This form should be filled out by
the CARG members who are 
requesting the reimbursement, and
then provided to Brant to fill in
the FOAPAL info and authorization.
If you need help, ask Brant.

\subsubsection{Direct Payments}
\label{sec:direct_payments}

If you need to be reimbursed for supplies, books, software, etc., the easiest way to achieve this is to purchase using a credit card and then submit a direct payment reimbursement using \href{http://cruzfly.ucsc.edu/}{CruzFly}. All purchases need to be authorized by Brant \emph{before they occur}. Again, we can only guaranteed reimbursements for pre-approved purchases following the university guidelines.

\subsubsection{Reappointments}
\label{sec:reappointments}

The UCSC PBScI Division handles reappointment requests for postdocs through the
\href{https://ucscforms.wufoo.com/forms/s1jkgiac0mds045/}{Postdoc Reappointment Form}.
Rearchers are reappointment through the  
\href{https://ucscforms.wufoo.com/forms/sta0lov0j8fq7s/}{Researcher Reappointment Form}. Reappointments require
a signed \href{https://apo.ucsc.edu/policy/capm/docs/610-000-appendix-e.pdf}{annual evaluation form} to be completed and submitted with the reappointment request.
