\section{Mentoring Agreements}
\label{sec:mentoring_agreement}

If you would like to develop a Mentoring Agreement to clarify the
professional relationship and goals related to working in the
Computational Astrophysics Research Group, we are happy to develop one.
We provide below an example Mentoring Agreement created by the
\href{https://graddiv.ucsc.edu/current-students/teaching-resources/citl-info.html}{UCSC Center for Innovations in Teaching and Learning} that we can adapt to best support your 
collaboration in the CARG. Many of the topics are already
outlined elsewhere within this Manual, but a Mentoring Agreement
can helpfully augment these policies by tailoring terms to
your needs.


\subsection{Example Mentoring Agreement}

This document provides an adaptable structure and set of topics to discuss when setting up a mentorship relationship. Both mentors and mentees can review their responses to these questions and work together to establish guidelines for their mentorship relationship, toward the end of supporting the mentee to succeed in their research program and to make progress toward their personal and professional goals. This document can be developed collaboratively and revisited whenever necessary.


\begin{enumerate}

\item  Shared Goals \& Vision (List the goals of this working relationship. What do you both hope to get out of working together? What skills and experience will the mentee gain through the project, and how will that learning serve their larger academic, personal, professional goals?)

\begin{itemize}	
\item Research project goals:
\item Mentee’s personal/professional goals:
\item Mentor’s personal/professional goals: 
\item Shared vision of success for this project: 
\end{itemize}

\item Approaches/Strategies/Steps to achieving listed goals (What do you both need to do to meet the above goals? Who is responsible for what actions?)
 
\begin{itemize}
\item Mentor’s role/tasks:
\item Mentee’s role/tasks:
\end{itemize}
 

\item Meeting Practices (Frequency, duration, format and platform for meetings, who will schedule the meetings, etc.)



\item Meeting Preparation (What will the mentee do to prepare for meetings? What will the mentor do to prepare for meetings?)
 
 
 
\item Communication Etiquette (How will the mentor and mentee communicate between meetings? Establish preferred modes of contact, timeframe for responsiveness, when to contact faculty mentor v. when to contact graduate student mentor, etc.)



\item Unplanned Issues (How will the mentor and mentee address unplanned issues that come up? For example, if the mentee gets stuck while working on the project, what are some steps they can take?)



\item Confidentiality Concerns (Ensure you are on the same page in terms of keeping particular discussions in confidence. If there are topics which either of you feel are off-limits for discussion, those can be named.)
 
 \end{enumerate}



